Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-04-29 PaperVictor.tex
Agregue - a todas las palabras quasi-omnidirectional

\begin{abstract}
We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide spectral range. Two techniques,
chirping (a continuous change in thicknesses) and stacking of
Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were carried out employing the
transfer matrix method and we optimized the design parameters to
obtain maximal reflectance averaged over different spectral ranges
for all angles. We fabricated some of the optimized structures with
porous silicon dielectric multilayers with low refractive contrast
and compared their measured  optical properties with the
calculations. Two chirped structures with thicknesses 21.6 $\mu$m
and 60.4 $\mu$m, resulting in quasi omnidirectional mirrors with
bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
respectively have been shown. In addition, we fabricated a stacked
sub-Bragg mirror structure  with a quasi omnidirectional bandwidth
of 1800 nm (centered at 1850 nm) and a thickness of 41.5 $\mu$m,
which is almost two third (in thickness) of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges. Our analysis techniques can be used for the
optimization of the reflectance not only in multilayered PS
systems  with different refractive index contrasts but also for
systems with other types of materials with low refractive index
contrast. The present study could also be useful for obtaining
omnidirectional dielectric mirrors in large spectral regions using
different materials,  flat focusing reflectors, thermal regulators,
or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.
\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands withiny a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

@@

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{F2Alternativa.pdf}
  \end{center}
  \caption{Reflectance spectra for non-polarized light calculated and measured at different
    angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
    $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
    (panel a)  and $S_2$ (panel b). The gray band indicates the
    region where the reflectance is greater than  $0.90$,
    corresponding to the quasi ODB of the
    structure. Inset: photograph of the synthesized structure.}
  \label{Fig2}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

Fig. \ref{Fig3}(a) reveals a quasi-ODM
in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which we attribute to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of
the synthesized structure, from 950 to 2750 nm, is slightly smaller than the calculated
one, the measured PBG is almost twice as wide
as a recently reported PS chirped structure \cite{Chavez2020}, which
has the largest previously reported ODW.

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM designed to operate in the NIR
region and their of the ODB's are compared with those of
the structures analyzed in the present study. The ODW
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
the ODB of the structure $S_3$ begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has an ODW 3.55 times higher. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies \cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
structure with large omnidirectional band with
the materials with relatively low refractive index contrast.

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&ODB (nm)&AR ($^\circ$)&ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
                \hline
                &    &$S_1$&980-1340&10-60&360 \\
                This work                               &2021&$S_2$&980-2780&10-60&1800\\
                &    &$S_3$&950-2750&10-60&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained omnidirectional bands (ODB) in the angular range (AR) and their widths (ODW).}
        \label{tab:table3}
\end{table}

@@

We have designed, optimized, fabricated and characterized highly reflective quasi
omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the reflectance with minimum thickness for a given pair of refractive indices. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a quasi
omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a
thickness of 41.5 $\mu$m, which is almost two third (in thickness)
of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could also be useful for obtaining omnidirectional dielectric mirrors in large spectral regions using different materials,  flat focusing reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

>>>>

\begin{abstract}
We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide spectral range. Two techniques,
chirping (a continuous change in thicknesses) and stacking of
Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were carried out employing the
transfer matrix method and we optimized the design parameters to
obtain maximal reflectance averaged over different spectral ranges
for all angles. We fabricated some of the optimized structures with
porous silicon dielectric multilayers with low refractive contrast
and compared their measured  optical properties with the
calculations. Two chirped structures with thicknesses 21.6 $\mu$m
and 60.4 $\mu$m, resulting in quasi-omnidirectional mirrors with
bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
respectively have been shown. In addition, we fabricated a stacked
sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
of 1800 nm (centered at 1850 nm) and a thickness of 41.5 $\mu$m,
which is almost two third (in thickness) of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges. Our analysis techniques can be used for the
optimization of the reflectance not only in multilayered PS
systems  with different refractive index contrasts but also for
systems with other types of materials with low refractive index
contrast. The present study could also be useful for obtaining
omnidirectional dielectric mirrors in large spectral regions using
different materials,  flat focusing reflectors, thermal regulators,
or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.
\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands within a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

@@

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{F2Alternativa.pdf}
  \end{center}
  \caption{Reflectance spectra for non-polarized light calculated and measured at different
    angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
    $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
    (panel a)  and $S_2$ (panel b). The gray band indicates the
    region where the reflectance is greater than  $0.90$,
    corresponding to the quasi-ODB of the
    structure. Inset: photograph of the synthesized structure.}
  \label{Fig2}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

Fig. \ref{Fig3}(a) reveals a quasi-ODM
in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which we attribute to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi-omnidirectional wavelength range of
the synthesized structure, from 950 to 2750 nm, is slightly smaller than the calculated
one, the measured PBG is almost twice as wide
as a recently reported PS chirped structure \cite{Chavez2020}, which
has the largest previously reported ODW.

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM and quasi-ODM designed to operate in the NIR
region and their (quasi) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
the quasi-ODB of the structure $S_3$ begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the quasi-ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to point out that the (quasi-) omnidirectional band widths of the
structures compared above correspond to different angular ranges,
which are defined by instrumental constrictions.

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&\emph{q}-ODB (nm)&AR (degrees)&\emph{q}-ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
                \hline
                &    &$S_1$&980-1340&10-60&360 \\
                This work&2021&$S_2$&980-2780&10-60&1800\\
                &    &$S_3$&950-2750&10-60&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained (quasi-) omnidirectional
                bands (\emph{q}-ODB), the measured angular range (AR) and their widths (\emph{q}-ODW).}
        \label{tab:table3}
\end{table}

@@

We have designed, optimized, fabricated and characterized highly reflective quasi-omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a
thickness of 41.5 $\mu$m, which is almost two third (in thickness)
of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.
